---
title: "st 115 homework 2"
author:
  - name: Nadeen Abdel-halim
    affiliation: NC State Univerisity
format: html
---

# Packages

## Question 1:

```{r eval = FALSE}
install.packages("aRtsy")
```

install.packages is used to install a package onto your device, while library is used to load that package into your current R session for use.

```{r}
library(aRtsy)
```

The Collatz sequence is used to take any positive number, divide it by 2 if it is even, or multiply it by 3 and add 1 if it is odd. This process repeats until 1 is reached.

## Question 2

```{r}
collatz <- function(n){
  sequence <- c(n)
  while (n > 1){
    if (n %% 2 == 0) {
      n <- n / 2
    } else {
      n <- 3*n+1
    }
    sequence <- c(sequence, n)
  }
  return(sequence)
}

```

## Question 3

```{r}
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```

This code created a blue drawing/sketch out of the number 10 based on Collatz.

The code produces a different output every time because it selects random starting numbers.

This can be an issue in a Quarto document because it causes reproducibility issues every time you render,

set.seed generates a random number that can be saved used to get the same result every time by setting an exact starting point for every run/render.

```{r}
set.seed(11)
canvas_collatz(
  colors = c("blue"),
  n = 10
)
```
